Uncertain database management has been studied extensively, and skyline query over uncertain database provides many significant applications, such as multi-criteria decision-making over uncertain data. Given an uncertain dataset containing k-dimensional objects, each object is represented by a weighted set of tuples called instances and follows a discrete probabilistic distribution. Probabilistic skyline computation finds the probability of each object being in the skyline set, or its skyline probability. A number of efficient algorithms~\cite{pei2007}~\cite{atallah2009}~\cite{bohm2009}~\cite{kim2011} have been proposed for Probabilistic skyline evaluation, but they all focus on solving the problem in a single machine.

Besides, when comes to skyline query for large datasets, the straightforward approach is to parallel the skyline processing, which also has drawn a lot of interests recently~\cite{ref:SkylineQueries}~\cite{ref:SkylineMulticore}~\cite{ref:SkylineDistributed}~\cite{ref:RandomPartition}. However, All previous algorithms are concentrated on paralleling the traditional skyline query, not probabilistic skyline query. In this paper, we focus on evaluating the probabilistic skyline query over uncertain database using MapReduce~\cite{ref:MapReduce}. In addition, mapreduce has been incorporated into increasing number of database applications~\cite{ref:KNNMapReduce}~\cite{ref:KNNJoin}~\cite{ref:SetSimilarity}~\cite{ref:ThetaJoins}.

Our work is most related to ~\cite{ding2012}, as they also concentrated on distributed skyline queries over uncertain data. However, Ding et al.~\cite{ding2012} assumes that every tuple in distributed uncertain database is attached with a probability, which could be regraded as a bivariate distribution, rather than multivariate distribution. Obviously the assumption is not in accord with real world. In addition, their algorithm can not be evaluated in mapreduce architecture, and is not efficient.


%\subsection{Motivations}
